Positive Results in Registered Reports

### 2020-01-11 manuscript/manuscript.tex
1. added a robustness check to the quantitative analysis script, 2. reorganised the folder structure (in accordance with Psych-DS), 3. changed code in the manuscript Rmd and in the analysis scripts to accommodate the new folder structure, 4. added the preregistration document with comments indicating adherence/deviations, 5. added a file with the full list of Psych journals from the ESI database
Added figure captions/notes; minor fixes

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  british,
  ,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Positive Results in Registered Reports},
  pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
  pdflang={en-UK},
  pdfkeywords={keyword 1, keyword 2, keyword 3},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\shorttitle{Positive Results in Registered Reports}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\else
  \usepackage[shorthands=off,main=british]{babel}
\fi

@@

Sterling (1959) already suspected a selection process behind the numbers he found:
\enquote{(\ldots) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Mahoney, 1977; Greenwald, 1975) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, n.d.).
These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``p-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).

@@

We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the RR population.
We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
An overview of the sampling process and all exclusions are shown in Figure 1.

For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (not specified in our preregistration, but no other seeds were tried).
We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig. 1).

\begin{figure}
\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{XXX ADD CAPTION}\label{fig:unnamed-chunk-2}
\end{figure}

For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
We downloaded a database of published RRs curated by the Center for Open Science{[}\^{}1{]} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
{[}\^{}1{]}: \url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}
Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
Following these exclusions, we verified the RR status of all remaining papers in our sample.
Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig. 1).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing {[}(``Registered Replication Reports,'' n.d.); decision was not preregistered{]}.

@@

Selecting papers that use the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} might yield different results than alternative search phrases.
Getting a better overview of \enquote{natural} descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's (2010) results and could inspire new research questions.
We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases.
If MS and AS had coded different hypothesis quotes for a paper, MS's coding was used, unless disagreement resolution of the \enquote{hypothesis support} variable lead to AS's coding overruling MS's.

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of RRs to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in RRs could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf.~Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
Conceptual replications and internal replications were not counted as replications in this narrow sense:
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
AS coded all papers, DL double-coded 32 RRs (\(45.07 \%\)) and 99 SRs (\(21.05 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

146 out of 152 SRs and 31 out of 71 RRs had positive results, meaning that the positive result rate was \(96.05 \%\) for SRs (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for RRs (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig. 1).
The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\label{fig:unnamed-chunk-5}Positive result rates for standard reports and Registered Reports. Error bars indicate 95\% confidence intervals around the observed positive result rate.}
\end{figure}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-6}Positive results in original studies vs replication studies}
\begin{tabular}{lrrrrrrrr}
\toprule
 & \multicolumn{4}{c}{original studies} & \multicolumn{4}{c}{replication studies} \\
\cmidrule(r){2-5} \cmidrule(r){6-9}
 & n & supported & \% & 95\% CI & n & supported & \% & 95\% CI\\
\midrule
SRs & 148 & 142 & 95.95 & 91.39; 98.50 & 4 & 4 & 100.00 & 39.76; 100.00\\
RRs & 30 & 15 & 50.00 & 31.30; 68.70 & 41 & 16 & 39.02 & 24.20; 55.50\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} SRs = standard reports, RRs = Registered Reports}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-8}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} This table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[british,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Positive Results in Registered Reports},
            pdfauthor={Anne Scheel, Mitchell Schijen, \& Daniël Lakens},
            pdfkeywords={keyword 1, keyword 2, keyword 3},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\shorttitle{Positive Results in Registered Reports}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\keywords{keyword 1, keyword 2, keyword 3\newline\indent Word count: XXX}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{float}
\usepackage{framed}
\usepackage{caption}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1, footnotesize}}
\captionsetup[textbox]{name=Box,labelsep=period,labelfont=it}
\newfloat{textbox}{thp}{lop}
\floatname{textbox}{Box}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=british]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\fi

@@

Sterling (1959) already suspected a selection process behind the numbers he found:
\enquote{(\ldots{}) for psychological journals a policy exists under which the vast majority of published articles satisfy a minimum criterion of {[}statistical{]} significance} (p.~31).
This selection process is one of several kinds of biases that will lead to an inflation of positive results in the literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts that find support for their tested hypotheses a higher chance of being published than manuscripts that do not find support for their tested hypotheses.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Mahoney, 1977; Greenwald, 1975) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make the evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to an inflated type-I error rate, see also Lakens, n.d.).
These include presenting unexpected results as having been predicted a priori (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``p-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been shown in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; John, Loewenstein, \& Prelec, 2012).

@@

We used the same method as Fanelli (2010) to obtain a new sample of standard reports, but restricted year of publication to 2013-2018 to match the sample to the RR population.
We excluded papers if they were not complete, published, non-retracted articles (e.g., meeting abstracts, study protocols without results), if they did not test a hypothesis, or if they contained insufficient information to reach a coding decision.
An overview of the sampling process and all exclusions are shown in Figure~\ref{fig:sampling}.

For standard reports we downloaded a current version of the Essential Science Indicators (ESI) database (retrieved on 4th December 2018) and used Web of Science to search for articles published between 2013 and 2018 with a Boolean search query containing the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} and the ISSNs of all journals listed in the ESI Psychiatry/Psychology category.
Using the same sample size as Fanelli (2010), we randomly selected 150 papers from the 1919 search results using the sample() function in R and the seed \enquote{20190120} (not specified in our preregistration, but no other seeds were tried).
We initially excluded eight papers and replaced them (the decision to replace excluded papers was not preregistered) through the same random sampling procedure until 150 studies were found that met our criteria, but later found that two papers had erroneously been excluded, leading to a final sample size of 152 rather than 150 (see Fig.~\ref{fig:sampling}).

\begin{figure}
\includegraphics[width=\textwidth]{Sampling_exclusions_and_resampling} \caption{Sampling process and exclusions for standard reports and Registered Reports. Standard reports were accidentally oversampled: We initially excluded 8 papers and only after replacing them found that two had erroneously been excluded. \enquote{Preregistered}: study had been preregistered but was not a full RR; \enquote{results-blind review}: article had undergone results-blind peer review but was not a full RR (authors knew results before first submission); \enquote{ambiguous}: Four of these had been treated as RRs but used pre-existing data to which the authors had access before conducting their analyses, one had no explicit signs of an RR except for a 2.5-year delay between submission and acceptance. We chose to exclude these cases to be conservative.}\label{fig:sampling}
\end{figure}

For Registered Reports we aimed to include all published RRs in the field of Psychology that tested at least one hypothesis, regardless of whether or not they used the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)}.
We downloaded a database of published RRs curated by the Center for Open Science\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} (retrieved on 19th November 2018), and excluded papers published in journals that were listed in categories other than \enquote{Psychiatry/Psychology} or \enquote{Multidisciplinary} in the ESI.
Note that the decision to focus only on the Psychiatry/Psychology category meant excluding 13 RRs published in Cortex because the ESI counts this journal towards the separate category \enquote{Neuroscience and Behavior}.
Papers published in multidisciplinary journals and in journals not included in the ESI (e.g., Royal Society Open Science) were hand-coded by AS.
This deviates from our preregistration insofar as we had not specified how discipline membership would be determined.
Following these exclusions, we verified the RR status of all remaining papers in our sample.
Papers were counted as RRs if they were labelled as such by the journal itself and the journal submission guidelines made it clear that these submissions had been reviewed and received in-principle acceptance before the data collection (or analyses) of all studies in the paper had been conducted (in accordance with \url{https://cos.io/rr}).
For papers not clearly labelled as RRs we consulted relevant editorial publications (e.g., for special issues) or contacted the respective editors directly.
Of the 151 entries in the COS RR database, 55 were excluded because they belonged to a non-Psychology discipline, 12 because they were not certainly RRs, and 13 because they did not test hypotheses or contained insufficient information, leaving 71 RRs for the final analysis (see Fig.~\ref{fig:sampling}).
Note that we excluded all eight \enquote{Registered Replication Reports} (RRRs; Simons, Holcombe, \& Spellman, 2014; Simons, 2018) in our sample because this format explicitly focusses on effect size estimation and not hypothesis testing (``Registered Replication Reports,'' n.d., decision was not preregistered).

@@

Selecting papers that use the phrase \enquote{test\(^\ast\) the hypothes\(^\ast\)} might yield different results than alternative search phrases.
Getting a better overview of \enquote{natural} descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's (2010) results and could inspire new research questions.
We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases. .

@@

We also wanted to code if a study was a replication of a previously published one:
We expected a much larger proportion of RRs to be direct replications, many of which may have been motivated by scepticism of the original study.
A lower positive result rate in RRs could then be an effect of failed replications rather than an effect of safeguards against QRPs and publication bias.
After an initial coding attempt with ill-defined coding criteria lead to too many disagreements (described further in the Appendix), we developed the following strategy (not pre-registered):
We searched the full texts of all papers for the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Köhler \& Cortina, 2019; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019; Pridemore, Makel, \& Plucker, 2018), and for those that did contain it determined whether the first hypothesis was a close or direct replication of previously published work.
Conceptual replications and internal replications were not counted as replications in this narrow sense:
The reason to code replication status in the first place was the idea that direct replications of previous work may be motivated by replicators' scepticism in the hypothesis and thus have a low prior probability, whereas conceptual replications are usually considered as building on previous work rather than verifying it.
AS coded all papers, DL double-coded 32 RRs (\(45.07 \%\)) and 99 SRs (\(21.05 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

146 out of 152 SRs and 31 out of 71 RRs had positive results, meaning that the positive result rate was \(96.05 \%\) for SRs (\(95 \%\) CI {[}91.61, 98.54{]}) and \(43.66 \%\) for RRs (\(95 \%\) CI {[}31.91, 55.95{]}; see Fig.~\ref{fig:mainplot}).
The preregistered one-sided proportions test with an alpha level of \(5\%\) showed that this difference of \(-52.39 \%\) was statistically significant, \(\chi^2 = 77.96\), \(p < .001\).
Unsurprisingly, the difference was not statistically equivalent to a range between \(-6 \%\) and \(6 \%\) at \(\alpha = 5\%\), \(z = 7.61\), \(p > .999\), meaning that we cannot reject differences more extreme than \(6\%\).
We thus accept our hypothesis that the positive result rate in RRs is lower than in SRs.

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/mainplot-1.pdf}
\caption{\label{fig:mainplot}Positive result rates for standard reports and Registered Reports. Error bars indicate \(95 \%\) confidence intervals around the observed positive result rate.}
\end{figure}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-4}Positive results in original studies vs replication studies}
\begin{tabular}{lrrrrrrrr}
\toprule
 & \multicolumn{4}{c}{original studies} & \multicolumn{4}{c}{replication studies} \\
\cmidrule(r){2-5} \cmidrule(r){6-9}
 & n & supported & \% & 95\% CI & n & supported & \% & 95\% CI\\
\midrule
SRs & 148 & 142 & 95.95 & 91.39; 98.50 & 4 & 4 & 100.00 & 39.76; 100.00\\
RRs & 30 & 15 & 50.00 & 31.30; 68.70 & 41 & 16 & 39.02 & 24.20; 55.50\\
\bottomrule
\addlinespace
\end{tabular}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} SRs = standard reports, RRs = Registered Reports}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

@@

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-6}Hypothesis introduction phrases in original Registered Reports (testing new hypotheses)}
\footnotesize{
\begin{tabular}{llrrr}
\toprule
 &  & \multicolumn{3}{c}{source} \\
\cmidrule(r){3-5}
core word(s) & introduction phrase & abstract & full text & total\\
\midrule
hypothes* &  & 5 & 12 & 17\\
 & (Hypothesis 1) & 0 & 1 & 1\\
 & Hypothesis 1 (H1): & 0 & 2 & 2\\
 & Hypothesis 1: & 0 & 1 & 1\\
 & Hypothesis 1a (H1a): & 0 & 1 & 1\\
 & hypothesis was & 0 & 1 & 1\\
 & Hypothesis: & 0 & 1 & 1\\
 & hypothesize that & 0 & 3 & 3\\
 & hypothesized that & 4 & 2 & 6\\
 & registered ... hypotheses & 1 & 0 & 1\\ \midrule
hypothes*, test* &  & 3 & 2 & 5\\
 & test of ... hypotheses & 0 & 1 & 1\\
 & test of ... hypothesis & 1 & 0 & 1\\
 & test the hypothesis that & 1 & 0 & 1\\
 & tested ... hypotheses & 0 & 1 & 1\\
 & tested the hypothesis that & 1 & 0 & 1\\ \midrule
test* &  & 5 & 2 & 7\\
 & test if & 0 & 1 & 1\\
 & test whether & 1 & 1 & 2\\
 & tested whether & 2 & 0 & 2\\
 & testing & 1 & 0 & 1\\
 & to ... test & 1 & 0 & 1\\ \midrule
test*, predict* & test ... prediction & 0 & 1 & 1\\ \midrule
examin* &  & 5 & 0 & 5\\
 & examine whether & 2 & 0 & 2\\
 & examined & 1 & 0 & 1\\
 & examined whether & 1 & 0 & 1\\
 & to examine & 1 & 0 & 1\\ \midrule
predict* &  & 4 & 0 & 4\\
 & had ... predictions & 1 & 0 & 1\\
 & predicted that & 2 & 0 & 2\\
 & predicts that & 1 & 0 & 1\\ \midrule
(other) &  & 0 & 5 & 5\\
 & (H1) & 0 & 1 & 1\\
 & expected that & 0 & 1 & 1\\
 & if ... then & 0 & 1 & 1\\
 & predication that & 0 & 1 & 1\\
 & we expect & 0 & 1 & 1\\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 44 hypothesis introduction phrases from 30 Registered Reports: 19 papers contributed one phrase each, nine papers contributed two each, one contributed three, and one contributed four.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:unnamed-chunk-7}Hypothesis introduction phrases in replication Registered Reports (testing previously studied hypotheses)}
\scriptsize{
\begin{tabular}{lllrrrr}
\toprule
 &  &  & \multicolumn{3}{c}{source}  &\\
\cmidrule(r){4-6}
 & core word(s) & introduction phrase & abstract & full text & total & \\
\midrule
 & hypothes* &  & 2 & 5 & 7 & \\
 &  & according to ... hypothesis & 0 & 1 & 1 & \\
 &  & Hypotheses & 0 & 1 & 1 & \\
 &  & Hypothesis 1 (H1): & 0 & 1 & 1 & \\
 &  & hypothesize that & 0 & 1 & 1 & \\
 &  & hypothesized that & 2 & 1 & 3 & \\ \midrule
 & hypothes*, test* &  & 2 & 1 & 3 & \\
 &  & test ... hypotheses & 0 & 1 & 1 & \\
 &  & test ... hypothesis & 1 & 0 & 1 & \\
 &  & tested ... hypotheses & 1 & 0 & 1 & \\ \midrule
 & hypothes*, examin* & examined ... hypothesis & 1 & 0 & 1 & \\ \midrule
 & hypothes*, predict* & hypotheses predicted & 1 & 0 & 1 & \\ \midrule
 & replicat* &  & 20 & 3 & 23 & \\
 &  & aim ... to replicate & 0 & 1 & 1 & \\
 &  & aim at replicating & 1 & 0 & 1 & \\
 &  & aimed to replicate & 0 & 1 & 1 & \\
 &  & attempted to replicate & 1 & 0 & 1 & \\
 &  & attempts to replicate & 1 & 0 & 1 & \\
 &  & conducted ... replication & 3 & 0 & 3 & \\
 &  & conducted ... replications & 2 & 0 & 2 & \\
 &  & performed ... replication & 2 & 0 & 2 & \\
 &  & present ... replication & 1 & 0 & 1 & \\
 &  & present ... replications & 1 & 0 & 1 & \\
 &  & replicated ... experiment & 1 & 0 & 1 & \\
 &  & replicating & 0 & 1 & 1 & \\
 &  & report ... replication attempt & 1 & 0 & 1 & \\
 &  & report ... replications & 2 & 0 & 2 & \\
 &  & sought to replicate & 3 & 0 & 3 & \\
 &  & we replicated & 1 & 0 & 1 & \\ \midrule
 & replicat*, examin* & critically examine and replicate & 1 & 0 & 1 & \\ \midrule
 & test* &  & 4 & 0 & 4 & \\
 &  & testing whether & 2 & 0 & 2 & \\
 &  & to ... test & 1 & 0 & 1 & \\
 &  & to test & 1 & 0 & 1 & \\ \midrule
 & examin* & examine whether & 0 & 1 & 1 & \\ \midrule
 & predict* & predicted that & 2 & 0 & 2 & \\ \midrule
 & (other) &  & 4 & 6 & 10 & \\
 &  & establish whether & 0 & 1 & 1 & \\
 &  & H1 & 0 & 2 & 2 & \\
 &  & investigate if & 1 & 0 & 1 & \\
 &  & sought to reproduce & 1 & 0 & 1 & \\
 &  & suggests that & 2 & 0 & 2 & \\
 &  & we ... conducted & 0 & 1 & 1 & \\
 &  & we assume & 0 & 1 & 1 & \\
 &  & we expect & 0 & 1 & 1 & \\
\bottomrule
\addlinespace
\end{tabular}
}
\begin{tablenotes}[para]
\normalsize{\textit{Note.} Table contains 53 hypothesis introduction phrases from 40 Registered Reports. One additional RR had no hypothesis introduction. Thirty papers contributed one phrase each, seven contributed two each, and three contributed three each.}
\end{tablenotes}
\end{threeparttable}
\end{center}
\end{table}
